fGFPCA dynamic prediction

### 2022-11-15 f-GFPCA.Rmd
modify in-sample formula

@@

```{r}
par(mfrow=c(3, 2))
## mean functions
plot(mid, fpca_fit$mu, ylab = "mean")

## eigenfunctions
plot(mid, fpca_fit$efunctions[, 1], ylab='PC1')
plot(mid, fpca_fit$efunctions[, 2], ylab='PC2')
plot(mid, fpca_fit$efunctions[, 3], ylab='PC3')
plot(mid, fpca_fit$efunctions[, 4], ylab='PC4')
```

@@

$$\hat{\boldsymbol{\xi}} = E(\boldsymbol{\xi}|\boldsymbol{Y}) =  \boldsymbol{\hat{\Gamma}\Phi ^T}(\boldsymbol{\Phi\hat{\Gamma}\Phi^T}+\hat{\sigma_{\epsilon}}^2\boldsymbol{I_m})^{-1}\boldsymbol{Y}$$
Where $\hat{\boldsymbol{\Gamma}}$ is the diagonal matrix of eigenvalues, $\boldsymbol{\Phi}$ is the matrix of eigenfunctions. These should be constant across all subjects.

>>>>

#### FPCA

@@

```{r, fig.height=12, fig.width=8}
par(mfrow=c(3, 2))
## mean functions
plot(mid, fpca_fit$mu, ylab = "mean")

## eigenfunctions
plot(mid, fpca_fit$efunctions[, 1], ylab='PC1')
plot(mid, fpca_fit$efunctions[, 2], ylab='PC2')
plot(mid, fpca_fit$efunctions[, 3], ylab='PC3')
plot(mid, fpca_fit$efunctions[, 4], ylab='PC4')
```
#### Estimated latent function

@@

$$\hat{\boldsymbol{\xi}} = E(\boldsymbol{\xi}|\boldsymbol{Y}) =  \boldsymbol{\hat{\Gamma}\Phi ^T}(\boldsymbol{\Phi\hat{\Gamma}\Phi^T}+\hat{\sigma_{\epsilon}}^2\boldsymbol{I_m})^{-1}(\hat{\boldsymbol{\eta}}-\hat{\boldsymbol{f}}_0)$$
Where $\hat{\boldsymbol{\Gamma}}$ is the diagonal matrix of eigenvalues, $\boldsymbol{\Phi}$ is the matrix of eigenfunctions. These should be constant across all subjects.
